Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-10 WSSSPE3/report/WSSSPE3_review.tex
Section 1-3:  Line breaks. No change in conetent.
Section 4: Fix open quotes.

\item \textbf{Dan Gunter, Sarah Poon and Lavanya Ramakrishnan: \textit{Bringing
the User into Building Sustainable Software for Science}} Dan Gunter's main
question was, "What is needed to develop sustainable software?". Beyond the
usual suspects of funding, great developers, good design, and software
engineering practices, however, Dan placed the users. He explained this using a
traditional software development model starting from gathering requirements, and
reaching release through a design and development and testing phase. The main
deficiency that with this approach was pointed out to be the too-late
interaction with users. Instead, an alternative approach was proposed that, at
first, skips the development phase and repeatedly goes through requirement
gathering, design and user interaction/learning phases, and only eventually
starts development once an agreement is reached, leading to an increased user
satisfaction, higher adoption, and eventually to sustained software.

>>>>

\item \textbf{Dan Gunter, Sarah Poon and Lavanya Ramakrishnan: \textit{Bringing
the User into Building Sustainable Software for Science}} Dan Gunter's main
question was, ``What is needed to develop sustainable software?''. Beyond the
usual suspects of funding, great developers, good design, and software
engineering practices, however, Dan placed the users. He explained this using a
traditional software development model starting from gathering requirements, and
reaching release through a design and development and testing phase. The main
deficiency that with this approach was pointed out to be the too-late
interaction with users. Instead, an alternative approach was proposed that, at
first, skips the development phase and repeatedly goes through requirement
gathering, design and user interaction/learning phases, and only eventually
starts development once an agreement is reached, leading to an increased user
satisfaction, higher adoption, and eventually to sustained software.
